A comprehensive framework to capture the arcana of neuroimaging analysis

### 2019-03-12 manuscript/manuscript-export.tex
renamed DmriStudy to DwiStudy to match BIDS

The Arcana framework is distributed as a publicly available software
package via GitHub
(\href{http://github.com/MonashBI/arcana}{{http://github.com/MonashBI/arcana}})
and the Python Package Index (PyPI)
(\href{https://pypi.org/project/arcana/}{{http://pypi.org/project/arcana/}}).
Study classes for T1, T2* and diffusion weighted MRI data have been
implemented as part of the \emph{Biomedical imAgiNg ANAlysis (Banana)}
package
(\href{https://github.com/MonashBI/banana}{{http://github.com/MonashBI/banana}};
\href{http://pypi.org./project/banana}{{http://pypi.org./project/banana}}).
All three classes, \emph{T1wStudy}, \emph{T2starwStudy} and
\emph{DmriStudy}, inherit generic image analysis methods, such as
registration and brain extraction, from the base class \emph{MRIStudy}.
The T1Study and T2starStudy classes are aggregated into the
\emph{T2starwT1wStudy} MultiStudy class to combine analysis of T2* and
T1-weighted contrasts.

The DmriStudy class implements diffusion tensor metrics, FA and ADC, as
well as global tractography using streamlines tracking from the MRtrix
toolbox (Tournier et. al. 2010; Tournier et. al. 2012) (Figure 9).

>>>>

The Arcana framework is distributed as a publicly available software
package via GitHub
(\href{http://github.com/MonashBI/arcana}{{http://github.com/MonashBI/arcana}})
and the Python Package Index (PyPI)
(\href{https://pypi.org/project/arcana/}{{http://pypi.org/project/arcana/}}).
Study classes for T1, T2* and diffusion weighted MRI data have been
implemented as part of the \emph{Biomedical imAgiNg ANAlysis (Banana)}
package
(\href{https://github.com/MonashBI/banana}{{http://github.com/MonashBI/banana}};
\href{http://pypi.org./project/banana}{{http://pypi.org./project/banana}}).
All three classes, \emph{T1wStudy}, \emph{T2starwStudy} and
\emph{DwiStudy}, inherit generic image analysis methods, such as
registration and brain extraction, from the base class \emph{MRIStudy}.
The T1Study and T2starStudy classes are aggregated into the
\emph{T2starwT1wStudy} MultiStudy class to combine analysis of T2* and
T1-weighted contrasts.

The DwiStudy class implements diffusion tensor metrics, FA and ADC, as
well as global tractography using streamlines tracking from the MRtrix
toolbox (Tournier et. al. 2010; Tournier et. al. 2012) (Figure 9).

### 2019-03-12 manuscript/manuscript.tex
renamed DmriStudy to DwiStudy to match BIDS

The Arcana framework is distributed as a publicly available software
package via GitHub (\url{github.com/MonashBI/arcana}) and the
Python Package Index (PyPI) (\url{pypi.org/project/arcana/}).
Study classes for T1, T2* and diffusion weighted MRI data have been
implemented as part of the \emph{Biomedical imAgiNg ANAlysis (Banana)} package
(\url{github.com/MonashBI/banana}; \url{pypi.org./project/banana}).
All three classes, \emph{T1Study}, \emph{T2starStudy} and
\emph{DmriStudy}, inherit generic image analysis methods, such as
registration and brain extraction, from the base class \emph{MriStudy}.

The DmriStudy class implements the extraction of diffusion tensor metrics,
FA and ADC, as well as whole-brain tractography using streamlines tracking from the MRtrix
toolbox \citep{tournier_improved_2010,tournier_mrtrix:_2012} (Figure \ref{fig:dmri_study}).

@@

The T1Study, T2starStudy and DmriStudy classes are
aggregated into a single MultiStudy class,
\emph{ArcanaPaper} (Supplementary material), which is specialised to produce
the figures in the Results section of this manuscript. In order to warp the
vein atlases to the subject space for comparison with the SWI and QSM images,
nonlinear registration to Montreal Neurological Institute templates
\citep{grabner_symmetric_2006} is performed in the T1Study. The transform and warp
field from this registration are then mapped onto the `coreg\_to\_atlas\_mat` and
`coreg\_to\_atlas\_warp' specifications in the T2starStudy, as the registration of
T2*-weighted images to the MNI template is typically poor.
These transforms are combined with the linear transform from the
brain-extracted T2*-weighted magnitude image to the brain extracted T1-weighted image,
which requires the `brain' specification in the T1Study to be mapped
to the `coreg\_ref\_brain` specification in the T2starStudy.

>>>>

The Arcana framework is distributed as a publicly available software
package via GitHub (\url{github.com/MonashBI/arcana}) and the
Python Package Index (PyPI) (\url{pypi.org/project/arcana/}).
Study classes for T1, T2* and diffusion weighted MRI data have been
implemented as part of the \emph{Biomedical imAgiNg ANAlysis (Banana)} package
(\url{github.com/MonashBI/banana}; \url{pypi.org./project/banana}).
All three classes, \emph{T1Study}, \emph{T2starStudy} and
\emph{DwiStudy}, inherit generic image analysis methods, such as
registration and brain extraction, from the base class \emph{MriStudy}.

The DwiStudy class implements the extraction of diffusion tensor metrics,
FA and ADC, as well as whole-brain tractography using streamlines tracking from the MRtrix
toolbox \citep{tournier_improved_2010,tournier_mrtrix:_2012} (Figure \ref{fig:dmri_study}).

@@

The T1Study, T2starStudy and DwiStudy classes are
aggregated into a single MultiStudy class,
\emph{ArcanaPaper} (Supplementary material), which is specialised to produce
the figures in the Results section of this manuscript. In order to warp the
vein atlases to the subject space for comparison with the SWI and QSM images,
nonlinear registration to Montreal Neurological Institute templates
\citep{grabner_symmetric_2006} is performed in the T1Study. The transform and warp
field from this registration are then mapped onto the `coreg\_to\_atlas\_mat` and
`coreg\_to\_atlas\_warp' specifications in the T2starStudy, as the registration of
T2*-weighted images to the MNI template is typically poor.
These transforms are combined with the linear transform from the
brain-extracted T2*-weighted magnitude image to the brain extracted T1-weighted image,
which requires the `brain' specification in the T1Study to be mapped
to the `coreg\_ref\_brain` specification in the T2starStudy.
